Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications

### 2017-05-24 automatica/automatica.tex
fixed affiliations
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\author[abate]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
\author[bessa]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
\author[cattaruzza]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
\author[cordeiro]{Lucas Cordeiro}\ead{lucas.cordeiro@cs.ox.ac.uk},
\author[david]{Cristina David}\ead{cristina.david@cs.ox.ac.uk},
\author[kesseli]{Pascal Kessel}\ead{pascal.kesseli@stx.ox.ac.uk},
\author[kroening]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
\author[polgreen]{Elizabeth Polgreen}\ead{elizabeth.polgreen@linacre.ox.ac.uk}

\address[abate]{University of Oxford, UK}
\address[bessa]{Federal University of Amazonas, Brazil}
\address[cattaruzza]{University of Oxford, UK}
\address[cordeiro]{University of Oxford, UK}
\address[david]{University of Oxford, UK}
\address[kesseli]{University of Oxford, UK}
\address[kroening]{University of Oxford, UK}
\address[polgreen]{University of Oxford, UK}

>>>>

\author[oxford]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
\author[manaus]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
\author[oxford]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
\author[oxford,manaus]{Lucas Cordeiro}\ead{lucas.cordeiro@cs.ox.ac.uk},
\author[oxford]{Cristina David}\ead{cristina.david@cs.ox.ac.uk},
\author[oxford]{Pascal Kessel}\ead{pascal.kesseli@stx.ox.ac.uk},
\author[oxford]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
\author[oxford]{Elizabeth Polgreen}\ead{elizabeth.polgreen@linacre.ox.ac.uk}

\address[oxford]{University of Oxford, UK}
\address[manaus]{Federal University of Amazonas, Brazil}
